Model of lens candidates from Space Warps CFHTLS

### 2016-07-08 paper2.tex
editing

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. Kueng et al.]{
Rafael Kueng,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
Presenjit Saha,$^{1}$
Lucy Oswald$^{3}$
%and Fourth Author$^{4}$
\\
% List of institutions
$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling modelling effort to
reconstruct their mass distributions.

To prepare for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in lens discovery through Space~Warps, as well as
several other projects involving astronomical data.  The style of
collaboration differs, however, from Space~Warps itself.  Space~Warps
works by sourcing a simple task to very large crowd

2016MNRAS.455.1171M,

One idea for coping with the challenge of modelling many more lenses
is to enlist the help of citizen scientists, a comm

 have between them discovered an average of

\section{Lens Modelling}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. Kueng et al.]{
Rafael Kueng,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
Prasenjit Saha,$^{1}$
Lucy Oswald$^{3}$
%and Fourth Author$^{4}$
\\
% List of institutions
$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling modelling effort to
reconstruct their mass distributions.  To prepare for the challenge of
massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
new modelling strategy, implemented as the SpaghettiLens system.  The
idea is to collaborate with experienced members of the citizen-science
community, who have already participated in lens discovery through
Space~Warps, as well as several other projects involving astronomical
data.  In this paper, we present SpaghettiLens models of
lens-candidates discovered through Space~Warps.

While SpaghettiLens is citizen science and based on Space~Warps, the
collaboration with volunteers takes a very different form.  In
Space~Warps, volunteers in a crowd of $\gtrsim10^4$ make independent
contributions.  Each person is presented with a random selection of
survey-patches and invited to (in effect) vote on each.  The system
estimates each volunteer's skill level according to test-patches
interspersed with the real data, and weights their votes accordingly
\citep{2016MNRAS.455.1171M}.  There is an active forum for volunteers,
but since everyone is seeing different data samples with minimal
overlap, the forum has little if any influence on votes.  With
SpaghettiLens there is a small group of volunteers and their
contributions are interdependent.\footnote{For more on how this works,
  see ``Collaborative gravitational lens modelling\dots'' in {\tt
    http://letters.zooniverse.org} especially the model tree.}

Section~\ref{sec:spl}

\section{Lens Modelling}\label{sec:spl}
